Human Deamination Read Length Analysis

### 2022-05-11 R/HumanDeaminationReadLengthAnalysis.rmd
Update HumanDeaminationReadLengthAnalysis.rmd

```{r enrichment_test_1}
for (i in 1:5) {
  testTable = data.table(Read_Length = 9,
                         Read_Sequence = replicate(1000, paste0(sample(c('A','C','G','T'), 9, TRUE), collapse = '')))
  testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
  testEnrichment = getSequenceEnrichmentByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
  plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
}
```

```{r enrichment_test_2}
for (i in 1:5) {
  testTable = data.table(Read_Length = 9,
                         Read_Sequence = replicate(1000,
                                                   paste0(sample(c(rep('A',6),rep('C',4),rep('G',4),rep('T',6)),
                                                                 9, TRUE), collapse = '')))
  testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
  testEnrichment = getSequenceEnrichmentByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
  plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
}
```

>>>>

```{r enrichment_test_1}
for (i in 1:5) {
  testTable = data.table(Read_Length = 9,
                         Read_Sequence = replicate(1000, paste0(sample(c('A','C','G','T'), 9, TRUE), collapse = '')))
  testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
  testEnrichment = getSequenceFreqByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
  plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
}
```

```{r enrichment_test_2}
for (i in 1:5) {
  testTable = data.table(Read_Length = 9,
                         Read_Sequence = replicate(1000,
                                                   paste0(sample(c(rep('A',6),rep('C',4),rep('G',4),rep('T',6)),
                                                                 9, TRUE), collapse = '')))
  testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
  testEnrichment = getSequenceFreqByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
  plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
}
```
